Quantifying the global film festival circuit: networks, diversity and value creation

### 2023-02-08 cudan/paperplots.qmd
update

examplefests = c("Festival de Cannes", "Sundance", "Hot Docs Festival", "Sitges FF", "Busan IFF", "BAFICI")

@@

```{r test, eval=F}
divyearplot(nodelist  %>% mutate(target=degree),ex=NULL, yl="Raw degree", convert=convertplots)
divyearplot(nodelist  %>% mutate(target=degree, lower=NA, upper=NA), 
            ex=examplefests, yl="Raw degree", convert=convertplots, splitab=F, 
            networkstats = T)

@@

```{r}
divyearplot(nodelist  %>% mutate(target=degree),ex=NULL, yl="Raw degree", convert=convertplots)
divyearplot(nodelist  %>% mutate(target=degree, lower=NA, upper=NA), 
            ex=examplefests, yl="Raw degree", convert=convertplots, splitab=F, 
            networkstats = T)

@@

```{r}
divyearplot(nodelist  %>% mutate(target=lndegree),ex=NULL, yl="Degree normalized by entry size", convert=convertplots)
divyearplot(nodelist  %>% mutate(target=lndegree, lower=NA, upper=NA), 
            ex=examplefests, yl="Degree normalized", convert=F, splitab=F, 
            networkstats = T)

@@

divyearplot(festgenrevecs  %>% mutate(target=indiv),
            ex=NULL, yl="Internal genre diversity", convert=convertplots, networkstats = F)
divyearplot(festgenrevecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=examplefests, yl="Internal genre diversity", convert=T, splitab=F, networkstats = F)

divyearplot(festgenrevecs  %>% mutate(target=exdiv),ex=NULL, yl="External genre diversity", convert=convertplots, networkstats = F)
divyearplot(festgenrevecs  %>% mutate(target=exdiv, lower=elower, upper=eupper), 
            ex=examplefests, yl="External genre diversity", convert=convertplots, splitab=F, networkstats = F)

@@

divyearplot(yeardiffvals  %>% mutate(target=yearmean, lower=yearmean-yearsd, upper=yearmean+yearsd), 
            ex=examplefests, yl="Time distance", convert=F, splitab=F, networkstats = F)

@@

divyearplot(festlangvecs  %>% mutate(target=indiv),ex=NULL, yl="Internal language diversity", convert=convertplots, networkstats = F)
divyearplot(festlangvecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=examplefests, yl="Language diversity", convert=convertplots, splitab=F, networkstats = F)

divyearplot(festlangvecs  %>% mutate(target=exdiv),
            ex=NULL, yl="External language diversity", convert=convertplots, networkstats = F)
divyearplot(festlangvecs  %>% mutate(target=exdiv, lower=elower, upper=eupper), 
            ex=examplefests, yl="External language diversity", convert=convertplots, splitab=F, networkstats = F)

@@

```{r}
divyearplot(festcountryvecs  %>% mutate(target=indiv),ex=NULL, yl="Internal geo diversity", convert=convertplots, networkstats = F)
divyearplot(festcountryvecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=examplefests, yl="Internal geo diversity", convert=convertplots, splitab=F, networkstats = F)

divyearplot(festcountryvecs  %>% mutate(target=exdiv),
            ex=NULL, yl="External geo diversity", convert=convertplots, networkstats = F)
divyearplot(festcountryvecs  %>% mutate(target=exdiv, lower=elower, upper=eupper), 
            ex=examplefests, yl="External geo diversity", convert=convertplots, splitab=F, networkstats = F)

@@

divyearplot(festcountryvecs  %>% mutate(target=eventdist),ex=NULL, yl="distance between latent centre and host country", convert=convertplots, networkstats = F)
divyearplot(festcountryvecs  %>% mutate(target=eventdist, lower=edlower, upper=edupper), 
            ex=examplefests, yl="distance", convert=convertplots, splitab=F, networkstats = F)

>>>>

exgenfests = c("Festival de Cannes", "Sundance", "Hot Docs Festival", "Sitges FF")
exgeofests = c("Festival de Cannes", "Sundance", "Tokyo IFF", "Zurich FF")
exlangfests=c("Festival de Cannes", "Sundance", "Busan IFF", "BAFICI")

@@

```{r test, eval=F}
divyearplot(nodelist  %>% mutate(target=degree),ex=NULL, yl="Raw degree", convert=convertplots)
divyearplot(nodelist  %>% mutate(target=degree, lower=NA, upper=NA), 
            ex=exgenfests, yl="Raw degree", convert=convertplots, splitab=F, 
            networkstats = T)

@@

```{r}
divyearplot(nodelist  %>% mutate(target=degree),ex=NULL, yl="Raw degree", convert=convertplots)
divyearplot(nodelist  %>% mutate(target=degree, lower=NA, upper=NA), 
            ex=exgenfests, yl="Raw degree", convert=convertplots, splitab=F, 
            networkstats = T)

@@

```{r}
divyearplot(nodelist  %>% mutate(target=lndegree),ex=NULL, yl="Degree normalized by entry size", convert=convertplots)
divyearplot(nodelist  %>% mutate(target=lndegree, lower=NA, upper=NA), 
            ex=exgenfests, yl="Degree normalized", convert=F, splitab=F, 
            networkstats = T)

@@

divyearplot(festgenrevecs  %>% mutate(target=indiv),
            ex=NULL, yl="Internal genre diversity", convert=convertplots, networkstats = F)
divyearplot(festgenrevecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=exgenfests, yl="Internal genre diversity", convert=T, splitab=F, networkstats = F)

divyearplot(festgenrevecs  %>% mutate(target=exdiv),ex=NULL, yl="External genre diversity", convert=convertplots, networkstats = F)
divyearplot(festgenrevecs  %>% mutate(target=exdiv, lower=elower, upper=eupper), 
            ex=exgenfests, yl="External genre diversity", convert=convertplots, splitab=F, networkstats = F)

@@

divyearplot(yeardiffvals  %>% mutate(target=yearmean, lower=yearmean-yearsd, upper=yearmean+yearsd), 
            ex=exgenfests, yl="Time distance", convert=convertplots, splitab=F, networkstats = F)

@@

divyearplot(festlangvecs  %>% mutate(target=indiv),ex=NULL, yl="Internal language diversity", convert=convertplots, networkstats = F)
divyearplot(festlangvecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=exlangfests, yl="Language diversity", convert=convertplots, splitab=F, networkstats = F)

divyearplot(festlangvecs  %>% mutate(target=exdiv),
            ex=NULL, yl="External language diversity", convert=convertplots, networkstats = F)
divyearplot(festlangvecs  %>% mutate(target=exdiv, lower=elower, upper=eupper), 
            ex=exlangfests, yl="External language diversity", convert=convertplots, splitab=F, networkstats = F)

@@

```{r}
divyearplot(festcountryvecs  %>% mutate(target=indiv),ex=NULL, yl="Internal geo diversity", convert=convertplots, networkstats = F)
divyearplot(festcountryvecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=exgeofests, yl="Internal geo diversity", convert=convertplots, splitab=F, networkstats = F)

divyearplot(festcountryvecs  %>% mutate(target=exdiv),
            ex=NULL, yl="External geo diversity", convert=convertplots, networkstats = F)
divyearplot(festcountryvecs  %>% mutate(target=exdiv, lower=elower, upper=eupper), 
            ex=exgeofests, yl="External geo diversity", convert=convertplots, splitab=F, networkstats = F)

@@

divyearplot(festcountryvecs  %>% mutate(target=eventdist),ex=NULL, yl="distance between latent centre and host country", convert=convertplots, networkstats = F)
divyearplot(festcountryvecs  %>% mutate(target=eventdist, lower=edlower, upper=edupper), 
            ex=exgeofests, yl="distance", convert=convertplots, splitab=F, networkstats = F)
